Can We Crunch the Social Graph on the Cheap?

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex
authors

@@

%todo format the UW names horizontally
\authorinfo{Jacob Nelson, Brandon Myers, A.H. Hunter, Dan Grossman, Mark Oskin,
Carl Ebeling, Luis Ceze}{University of Washington}{\{nelson, bdmyers, ahh, djg, oskin, ebelin, luisceze\}@cs.washington.edu}
\authorinfo{Simon Kahan}{Pacific Northwest National Lab}{skahan@cs.washington.edu}
\authorinfo{Preston Briggs}{}{preston.briggs@gmail.com}

\maketitle
\begin{abstract}
  Large, sparse, irregular graphs map poorly to the memory systems of
  commodity hardware. The scale of emerging real world datasets
  presents a challenge for straightforward algorithms which will run
  inefficiently due to many high-latency accesses.  Pervasive
  parallelism can tolerate that latency, but the only large-scale
  implementation of the technique is the Cray XMT, an expensive,
  non-commodity machine.

>>>>

%\textheight 9in
%\textwidth 6.5in
%\columnsep 1pc
\renewcommand{\baselinestretch}{0.9}

@@

%todo format the UW names horizontally
\authorinfo{Jacob Nelson, Brandon Myers, A.H. Hunter, Preston Briggs,
  Dan Grossman, Mark Oskin, Carl Ebeling, Simon Kahan, Luis
  Ceze}{University of Washington}{\{nelson, bdmyers, ahh, preston,
  djg, oskin, ebeling, skahan, luisceze\}@cs.washington.edu}

\maketitle

\begin{abstract}
  Large, sparse, irregular graphs map poorly to the memory systems of
  commodity hardware. The scale of emerging real world datasets
  presents a challenge for straightforward algorithms which will run
  inefficiently due to many high-latency accesses.  Pervasive
  parallelism can tolerate that latency, but the only large-scale
  implementation of the technique is the Cray XMT, an expensive,
  non-commodity machine.
